Results_paper1

### 2019-05-03 Paper1_results.Rmd
cleaned_script
progress

#Plotting the data
#SAWS data
ggplot(index, aes(x= date, y=ui.saws)) +
  geom_area(aes(fill=saws.condition)) +
  facet_wrap(~site) +
  geom_line() +
  geom_hline(yintercept=0)

index_SP <- index %>% 
  filter(site == "Sea Point") %>% 
  slice(-(c(34:70,435:632,686,1704)))

@@

@@

To do:
- Try PCA
- plot
- dave upwelling index
-

>>>>

#Plotting the data
#SAWS data
ggplot(index, aes(x= date, y=ui.saws)) +
  geom_area(aes(fill=saws.condition)) +
  facet_wrap(~site) +
  geom_hline(yintercept=0)

# Seperating sites
index_SP <- index %>% 
  filter(site == "Sea Point") %>% 
  slice(-(c(34:70,435:632,686,1704)))

@@

Calculating the temperature anomalies. This will be plotted on the same graph as the upwelling indeces. This allows for an observation on the relationship or patterns that exist as a result of temperature changes and he upwelling and downwelling conditions.

@@
